A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}

### 2019-12-11 4_method.tex
give bounds on width variation (reviewer 3.4)
add forgotten \revise
lil language fix

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
As illustrated in See \cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$. This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
Although significance measures are commonly used as a heuristic for finding the parts of a skeleton which are in some sense relevant~\cite{attali1996modeling,Sud2007},
we use the bisector angle as an \emph{exact} indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

We perform a filtering step to prevent frequently changing the bead count back and forth within a short distance.
For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).

>>>>

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
As illustrated in \revise{See }{}\cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$.
This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
Although significance measures are commonly used as a heuristic for finding the parts of a skeleton which are in some sense relevant~\cite{attali1996modeling,Sud2007},
we use the bisector angle as an \emph{exact} indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

We perform a filtering step to prevent frequently changing the bead count back and forth within a short distance.
For two consecutive anchors which transition to opposite directions, if the distance between them is smaller than some limit $d_\text{max}^\text{transition}$, the bead counts at all nodes in-between are set to the surrounding bead counts, and consequently these anchors are removed (See \cref{beading_transitioning_filtering__filtered}).
\revise{}{This means that for some small regions we generate toolpaths with bead widths outside the typical range.}
